---
title: "Figure 3C"
output:
  html_document:
    theme: readable
    df_print: paged
    code_folding: hide
    toc: true
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
options(stringsAsFactors = F)
seed <- 87532163

library(knitr)
library(ggplot2)
library(ggpointdensity)
library(RColorBrewer)
library(dplyr)
library(tidyr)
library(scales)

source("../bin/R_rainclouds.R")

# knitr::opts_knit$set(root.dir = "PLACEHOLDER")
knitr::opts_chunk$set(fig.width = 4, fig.height = 4, fig.show = "hold")

theme_set(theme_bw(base_size = 12))
```

```{r}

samples <- c( "abcu196_4", "lab_gm12878", "buenrostro_rep1", "hepg2_3")
labs <- c("Pancreatic islets", "GM12878\n(this study)", "GM12878\n(Buenrostro)",
          "HepG2")

d <- lapply(samples, function(i){
  sprintf("../data/processed/6-mers/%s.hamming.txt", i) %>% 
    read.table(header = T) %>% 
    mutate(sample = i)
  }) %>% 
  bind_rows() %>% 
  mutate(sample_ord = factor(sample, levels = samples, labels = labs, ordered = T))

d_summary <- d %>% 
  group_by(sample, kmer1) %>% 
  summarise(fvice = unique(fvice1), max = max(fvice2), min = min(fvice2)) %>% 
  mutate(range = abs(max - min)) %>% 
  mutate(range_signed = max - min) %>% 
  mutate(rel_max = abs(fvice - max), rel_min = abs(fvice - min)) %>% 
  mutate(sample_ord = factor(sample, levels = samples, labels = labs, ordered = T))
```

```{r, fig.width=8, fig.height=2.5, dev="cairo_pdf"}
# ```{r, fig.width=7, fig.height=5}
ggplot(d_summary, aes(x = rel_min, y = rel_max)) +
  geom_pointdensity() +
  geom_abline() +
  scale_color_viridis_c(trans = "log10", labels = comma) +
  facet_wrap(~ sample_ord, nrow = 1) + 
  labs(x = "Max f-VICE decrease relative to reference 6-mer", 
       y = "Max f-VICE increase relative to reference 6-mer", 
       color = "Density")

ggplot(d_summary, aes(range_signed)) +
  geom_histogram(color = "black", fill = "gray", bins = 30) +
  facet_wrap(~ sample_ord, nrow = 1) + 
  labs(x = "f-VICE difference range", y = "Count")
```

```{r, fig.width=8, fig.height=2.5, dev="cairo_pdf"}
# ```{r, fig.width=7, fig.height=5}
nt_pct <- function(kmer, nt = c("G", "C"), len = 6) {
  sum(unlist(strsplit(kmer, "")) %in% nt) / len
}

d_gc <- d_summary %>% 
  rowwise() %>% 
  mutate(gc = round(nt_pct(kmer1), 1)) %>% 
  ungroup() %>% 
  mutate(gc = factor(gc))

ggplot(d_gc, aes(x = gc, y = range_signed, group = gc)) +
  geom_flat_violin(position = position_nudge(x = 0, y = 0), adjust = 1, 
                   trim = FALSE, alpha = .5) +
  geom_point(aes(x = as.numeric(gc) - 0.3, y = range), 
             position = position_jitter(width = .10, height = 0),
             size = .25, alpha = .5) +
  geom_boxplot(aes(x = as.numeric(gc) + 0, y = range), 
               outlier.shape = NA, width = .15,color = "black") +
  facet_wrap(~ sample_ord, scales = "free_y", nrow = 1) + 
  labs(x = "GC content", y = "f-VICE range", color = "Density")
```

```{r, fig.width=8, fig.height=2.5, dev="cairo_pdf"}
pal <- rev(brewer.pal(9, "RdBu"))
pal[5] <- "gray"

d_gc %>% 
  mutate(gc = as.numeric(as.character(gc))) %>% 
  ggplot(aes(x = rel_min, y = rel_max, color = gc)) +
  geom_point(alpha = .5) +
  geom_abline() +
  scale_color_gradientn(colors = pal) +
  facet_wrap(~ sample_ord, nrow = 1) + 
  labs(x = "Max f-VICE decrease\n(relative to reference 6-mer)", 
       y = "Max f-VICE increase\n(relative to reference 6-mer)", 
       color = "6-mer\nGC content") +
  theme(panel.grid.minor = element_blank())

```
